\huge Tor's Usability for Censorship Circumvention

### 2016-04-14 pets2017-paper/pets2017-paper.tex
Add a figure with transport names.

>>>>

\begin{figure}
\small
\begin{itemize}
\renewcommand{\labelitemi}{$\circ$}
\item Connect with provided bridges\\
Transport type:
\begin{itemize}
\item flashproxy
\item fte
\item fte-ipv6
\item meek-amazon
\item meek-azure
\item meek-google
\item obfs3 (recommended)
\item obfs4
\item scramblesuit
\end{itemize}
\item Enter custom bridges\qquad\fbox{Help}\\
\end{itemize}
\caption{
Bridge selection options in Tor Browser~5.0.3.
The obscure strings under ``Connect with provided bridges'' denote various
built-in circumvention technologies (``pluggable transports'').
Under ``Enter custom bridges'', there is a space to paste in
a bridge specification that was obtained out of band.
The ``Help'' button displays instructions on obtaining such
bridge specifications.
}
\label{fig:bridge-options}
\end{figure}

Fig.~\ref{fig:bridge-options} shows the bridge options
presented to a user in Tor Browser~5.0.3.
